---
title: "Lecture 2 R Programming"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Week 0 Introduction

Setting/getting working directory

```{r}
getwd()
ls()
```

# Week 1 Getting Started

## Entering Input

```{r}
x <- 1
print(x) # this is a comment
msg <- "hello"
print(msg)
```

## Data Type

* character
* numeric
* integer
* complex
* logical

* Vector can only contain objects of the same class
* List can contain objetcs of different classes

Empty vectors: `vector()`

##Attricbutes

* names
* dimension
and so on

`attribute()`

##Creating a vector

```{r}
x <- c(T,F)
y <- vector("numeric", length = 10)
x
y
```


When different objects are mixed in a vector, every element is tranfered to the same class.

```{r}
x <- c(1.7, "a")
y <- c(T, 2)
z <- c("a", T)
class(x)
class(y)
class(z)
```

Explicit Coercion using `as.`

```{r}
x <- 0:6
as.numeric(x)
as.character(x)

```

## List

```{r}
x <- list(1,"a",T)
x
```

## Matrix

```{r}
m <- matrix(1:8, nrow = 2, ncol = 4)
m
dim(m)
attributes(m)
```

```{r}
m <- 1:10
m
dim(m) <- c(2,5)
m
```

```{r}
x <- 1:3
y <- 5:7
z <- cbind(x,y)
z
z <- rbind(x,y)
z
```

